---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TABLEONE

The goal of TABLEONE is to generate table 1 on study sample.

Major highlights include:

- Main variable could be variable format: continuous, binary or categorical (>2 levels).
- Perform statistical test depending on variable class: correlation/two-group t-test/ANOVA
- Output resulted table in both pdf and excel format.

## Installation

`TABLEONE` can be installed from [GitHub](https://github.com/ningb/TABLEONE) with:

``` r
# install.packages("devtools")
devtools::install_github("ningb/TABLEONE")
```
## Usage

### Generating table one with statistics

Here is a basic example. The `TABLEONE` pakcage includes a toy example study description. We will load it and examine the varaibles association with the cancer status:

```{r example}
library(TABLEONE)
data(index)
output <- tableone("Cancer", c(1:5), index)

output
```

### Output 

`TABLEONE` includes two types of output: pdf or excel (good for presentation and sharing):

```{r}
tableone.plot(output)
# tableone.export(output)
```
